---
title: "Steller sea lions in Atlantis GOA"
author: "Alberto Rovellini"
date: "10/27/2021"
output:
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
---

```{r}
library(readxl)
library(sdmTMB)
library(tidyverse)
library(rbgm)
library(sf)
library(viridis)
library(maps)
library(mapdata)
library(data.table)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
select <- dplyr::select
```

# Purpose

Explore Steller sea lion data for the GOA from Katie Sweenie and Brian Fadely. For citation, refer to Johnson, D., and L. Fritz. 2013. Pup/ Nonpup ratios in WDPS Steller sea lion population. Memo submitted to Alaska Science Center. August 2013. 17 pp.

Sites used by Steller sea lions are rookeries and haulouts. Rookeries are sites used during the breeding seasons where pups occur. Haulouts are used more consistently throughout the year by non-breeding adults and other ages. See [here](https://www.fisheries.noaa.gov/resource/data/steller-sea-lion-haulout-and-rookery-locations-united-states-may-5-2016). We will need to differentiate between these: females at the rookeries in the summer travel not too far from the colony, with much broader ranges in the winter time (17.1 km and 133 km on an average trip for females in summer and winter respectively, although for a small sample size in [Merrick and Loughlin 1997](https://doi.org/10.1139/z97-099)).

The range around the rookeries will be smaller than around the haulouts. To make matters more complicated, a rookery is also a haulout, and there can be pups at a rookery (the cutoff seems to be 50 pups). Therefore, rookery sites also count towards winter distributions. 

From communications with Katie Sweeney and others it seems that they no longer attempt to correct the counts to capture at-sea animals (they used to apply a correction factor way back but they have discontinued it because it was based on population estimates from the 1970's - there is ongoing research to re-evaluate this but way down the line).

This workflow uses data from Alaska and from British Columbia.

# Read data

## Alaska

Data shared by Katie Sweeney and Brian Fadely. These are aerial surveys conducted by the National Marine Mammal Laboratory (NMML). See [here](https://repository.library.noaa.gov/view/noaa/10474/noaa_10474_DS1.pdf) and references therein for information on the surveys. This data is used to conduct Steller sea lion stock assessments for the [Eastern](https://media.fisheries.noaa.gov/dam-migration/2019_sars_alaska_steller_sea_lion_-_eastern_us.pdf) and [Western](https://media.fisheries.noaa.gov/2021-08/STELLER%20SEA%20LION%20%28Eumetopias%20jubatus%29%20-%20Western%20U.S.%20Stock.pdf) GOA with the use of a [Bayesian modelling approach](https://besjournals.onlinelibrary.wiley.com/doi/pdf/10.1111/2041-210X.12231) to estimate missing counts.

```{r}
#SSL all
#pups
wdps_pup <- read_excel('../data/sslcountdata/GULF_SSLcountsRAW.xlsx', sheet = 'wdpspup')
edps_pup <- read_excel('../data/sslcountdata/GULF_SSLcountsRAW.xlsx', sheet = 'edpspup')

#non-pups
wdps_nonpup <- read_excel('../data/sslcountdata/GULF_SSLcountsRAW.xlsx', sheet = 'wdpsnp')
edps_nonpup <- read_excel('../data/sslcountdata/GULF_SSLcountsRAW.xlsx', sheet = 'edpsnp')

#correction factor for non-pups
corr <- read_excel('../data/sslcountdata/GULF_SSLcountsRAW.xlsx', sheet = 'edpsnp_corr')

# #pups
# wdps_pup <- read_excel('../data/sslcountdata/SSLGOA_rawcounts.xlsx', sheet = 'wdpspup')
# edps_pup <- read_excel('../data/sslcountdata/SSLGOA_rawcounts.xlsx', sheet = 'edpspup')
# 
# #non-pups
# wdps_nonpup <- read_excel('../data/sslcountdata/SSLGOA_rawcounts.xlsx', sheet = 'wdpsnp')
# edps_nonpup <- read_excel('../data/sslcountdata/SSLGOA_rawcounts.xlsx', sheet = 'edpsnp')
# 
# #correction factor for non-pups
# corr <- read_excel('../data/sslcountdata/SSLGOA_rawcounts.xlsx', sheet = 'edpsnp_corr')

# Sites
sites <- read.csv('../data/sites/NCEI-0129877_US_SSL_Sites.csv')

# Atlantis
atlantis_bgm <- read_bgm('../data/GOA_WGS84_V4_final.bgm')
atlantis_box <- atlantis_bgm %>% box_sf()
atlantis_crs <- atlantis_bgm$extra$projection
atlantis_bbox <- atlantis_box %>% st_bbox()
```

Process the raw data. 
```{r}
# apply correction to edps data
edps_nonpup_long <- edps_nonpup %>% pivot_longer(!c(SITE,REGION), names_to = 'YEAR', values_to = 'COUNTS')
corr_long <- corr %>% pivot_longer(!c(SITE,REGION), names_to = 'YEAR', values_to = 'CORRECTION')

edps_nonpup_long <- edps_nonpup_long %>% left_join(corr_long, by = c('SITE','REGION','YEAR')) %>%
  mutate(COUNTS=ifelse(CORRECTION==1,COUNTS*3.5,COUNTS)) %>%
  ungroup() %>% 
  select(-CORRECTION)

# pivot the remaining three datasets to long format
wdps_nonpup_long <- wdps_nonpup %>% pivot_longer(!c(SITE,REGION), names_to = 'YEAR', values_to = 'COUNTS')
wdps_pup_long <- wdps_pup %>% pivot_longer(!c(SITE,REGION), names_to = 'YEAR', values_to = 'COUNTS')
edps_pup_long <- edps_pup %>% pivot_longer(!c(SITE,REGION), names_to = 'YEAR', values_to = 'COUNTS')

# bind pups and non-pups 
nonpup_long <- rbind(wdps_nonpup_long,edps_nonpup_long)
pup_long <- rbind(wdps_pup_long,edps_pup_long)

# join coordinates from sites data
nonpup_long <- nonpup_long %>% left_join(sites %>% select(SITENAME,REGION,ROOKERY,LATITUDE,LONGITUDE), by = c('SITE'='SITENAME','REGION'='REGION'))
pup_long <- pup_long %>% left_join(sites %>% select(SITENAME,REGION,ROOKERY,LATITUDE,LONGITUDE), by = c('SITE'='SITENAME','REGION'='REGION'))

# coordinates for some sites are missing
missing_nonpup <- nonpup_long %>% filter(is.na(LONGITUDE)) %>% select(SITE) %>% distinct() %>% pull()
missing_pup <- pup_long %>% filter(is.na(LONGITUDE)) %>% select(SITE) %>% distinct() %>% pull()
missing <- sort(unique(c(missing_nonpup,missing_pup)))

# some missing names are more specific in the site data set than in the SSL counts. We can get those
# the missing sites also miss information on whether the site is a rookery or a haulout.

nonpup_long <- nonpup_long %>% # for non-pups
  rowwise() %>%
  mutate(LONGITUDE = ifelse(SITE %in% missing, sites[grep(pattern=SITE,x=sites$SITENAME)[1],]$LONGITUDE, LONGITUDE),
         LATITUDE = ifelse(SITE %in% missing, sites[grep(pattern=SITE,x=sites$SITENAME)[1],]$LATITUDE, LATITUDE)) %>% 
  ungroup()

pup_long <- pup_long %>% # and pups
  rowwise() %>%
  mutate(LONGITUDE = ifelse(SITE %in% missing, sites[grep(pattern=SITE,x=sites$SITENAME)[1],]$LONGITUDE, LONGITUDE),
         LATITUDE = ifelse(SITE %in% missing, sites[grep(pattern=SITE,x=sites$SITENAME)[1],]$LATITUDE, LATITUDE)) %>% 
  ungroup()

# some are still missing, enter coordinates manually
missing_nonpup1 <- nonpup_long %>% filter(is.na(LONGITUDE)) %>% select(SITE) %>% distinct()
missing_pup1 <- pup_long %>% filter(is.na(LONGITUDE)) %>% select(SITE) %>% distinct()
missing1 <- rbind(missing_nonpup1,missing_pup1) %>%
  mutate(LONGITUDE = c(-149.467,-156.639, -160.298,-167.073,-171.274,-130.616,-130.917,-130.967),
         LATITUDE = c(59.742,56.044,58.680,53.925,52.488,53.490,51.962,52.208)) 

# add to the data
nonpup_long <- nonpup_long %>% # for non-pups
  rowwise() %>%
  mutate(LONGITUDE = ifelse(SITE %in% missing1$SITE, missing1[missing1$SITE==SITE,]$LONGITUDE, LONGITUDE),
         LATITUDE = ifelse(SITE %in% missing1$SITE, missing1[missing1$SITE==SITE,]$LATITUDE, LATITUDE)) %>% 
  ungroup()

pup_long <- pup_long %>% # and pups
  rowwise() %>%
  mutate(LONGITUDE = ifelse(SITE %in% missing1$SITE, missing1[missing1$SITE==SITE,]$LONGITUDE, LONGITUDE),
         LATITUDE = ifelse(SITE %in% missing1$SITE, missing1[missing1$SITE==SITE,]$LATITUDE, LATITUDE)) %>% 
  ungroup()

# fill in the rookery column. If they are non-pup sites only, set ROOKERY=0, if pup ROOKERY=1. If both, set ROOKERY=1.
# this will need revision, because sites where pups were counted that appear in the pups set are labelled as ROOKERY=0. Approximate it for now.
only_nonpup <- setdiff(missing_nonpup,missing_pup)

nonpup_long <- nonpup_long %>%
  rowwise() %>%
  mutate(ROOKERY=ifelse(!is.na(ROOKERY),ROOKERY,ifelse(SITE %in% only_nonpup,0,1))) %>% 
  ungroup()

pup_long <- pup_long %>% # if pups are there, assume it is a rookery
  rowwise() %>% 
  mutate(ROOKERY=ifelse(!is.na(ROOKERY),ROOKERY,1)) %>% 
  ungroup()

# drop ST. GEORGE in E ALEU because it is a site in the BS that gets erroneously mapped to California
nonpup_long <- nonpup_long %>% filter(SITE!='ST. GEORGE')
```

View in space.
```{r, fig.width=12, fig.height=18}
nonpup_sf <- nonpup_long %>% st_as_sf(coords=c('LONGITUDE','LATITUDE'),crs=4326)
nonpup_bbox <- nonpup_sf %>% st_bbox()

coast <- maps::map("worldHires", c("USA","Canada"), plot = FALSE, fill = TRUE)
coast_sf <- coast %>% st_as_sf() %>% st_combine()

nonpup_sf %>% filter(YEAR>1989 & YEAR!='RCA') %>% 
  ggplot()+
  geom_sf(aes(color=COUNTS, shape=factor(ROOKERY)))+
  scale_color_viridis()+
  geom_sf(data=coast_sf)+
  coord_sf(xlim=c(nonpup_bbox$xmin,nonpup_bbox$xmax), ylim=c(nonpup_bbox$ymin,nonpup_bbox$ymax))+
  theme_minimal()+
  facet_wrap(~YEAR, ncol=3)+
  labs(title='Steller sea lion haulouts and rookeries in Alaska')
```
If we are after distributions in the 1990's use 1990-1999 and pool data from those years. Then use similar technique to the seabirds to draw circles around the colonies, depending on the foraging range. Then map those to the Atlantis boxes.

Need to read about trip distance and duration but it seems to change between males and females and also between seasons, which will allow us to capture where they go. 

Subset to data from the 1990's, take averages for each colony. 
```{r}
nonpup_sf <- nonpup_sf %>% filter(YEAR %in% (1971:1999)) # use the 90's

nonpup_avg_ak <- nonpup_sf %>% group_by(SITE,REGION,ROOKERY) %>% summarise(COUNTS=mean(COUNTS,na.rm=TRUE))

# NaN where all counts in the 1990's were NA's. Drop those altogether
nonpup_avg_ak <- nonpup_avg_ak %>% filter(!is.nan(COUNTS))

nonpup_avg_ak %>%  
  ggplot()+
  geom_sf(data=coast_sf)+
  geom_sf(aes(color=COUNTS, shape = factor(ROOKERY)), size=2)+
  scale_color_viridis()+
  coord_sf(xlim=c(nonpup_bbox$xmin,nonpup_bbox$xmax), ylim=c(nonpup_bbox$ymin,nonpup_bbox$ymax))+
  theme_minimal()+
  labs(title='Steller sea lion haulouts and rookeries in Alaska')
```

## British Columbia

Data from [DFO](https://open.canada.ca/data/en/dataset/0083baf1-8145-4207-a84f-3d85ef2943a5).

### Correction factor to account for animals at sea 

In [DFO 2020](https://waves-vagues.dfo-mpo.gc.ca/Library/40951753.pdf) we read: "Satellite telemetry data collected during summer indicated that peak numbers of animals are hauled out during daylight hours, and estimated that 67% of animals were hauled out during surveys conducted in the summer breeding season. A survey correction factor of 1.48 was therefore applied to non-pup counts. In contrast, animals spent less time on land during the non-breeding season, and haulout bouts were less synchronized. As a result, it is estimated that only 37% of animals were hauled out and counted during winter surveys". However, NOAA does not seem to apply the correction factor, so maybe we just stick to counts here as well. The data downloaded from DFO seem to come without correction factor (see [here](https://pacgis01.dfo-mpo.gc.ca/FGPPublic/Steller_sea_lion/SSL_Data_Dictionary.htm)).

```{r}
bc_data <- read.csv('../data/BC/Steller_Sea_Lion_Summer_counts_from_Haulout_Locations.csv')

bc_data <- bc_data %>%
  mutate(across(starts_with('COUNT'), as.numeric)) %>%
  filter(!is.na(LATITUDE))

# sum extrapolated and real values, then drop the extrapolated values
bc_data <- bc_data %>%
  rowwise() %>% # most of the time the below will result into NAs. Are those zeroes or missing counts?
  mutate(COUNT.NON.PUP = ifelse(is.na(COUNT.NON.PUP),COUNT.NON.PUP.INTERPOLATED.EXTRAPOLATED,COUNT.NON.PUP),
         COUNT.PUP = ifelse(is.na(COUNT.PUP),COUNT.PUP.INTERPOLATED.EXTRAPOLATED,COUNT.PUP),
         COUNT.PUP.PRE.ROOKERY = ifelse(is.na(COUNT.PUP.PRE.ROOKERY),COUNT.PUP.PRE.ROOKERY.INTERPOLATED.EXTRAPOLATED,COUNT.PUP.PRE.ROOKERY)) %>% 
  ungroup()
  
# long format
bc_long <- bc_data %>% pivot_longer(cols = starts_with('COUNT'), names_to = 'STAGE', values_to = 'COUNTS')
```

There seem to be more options regarding the site type here, with distinctions between rookeries, winter haulouts, year-round haulouts, and so on. Probably best simplify this to rookery and haulouts again. We also only really care about the non-pups here. Most (almost all?) pups seem to be found at the sites labelled as R or Y/R.
```{r}
bc_long <- bc_long %>% 
  rowwise() %>% 
  mutate(ROOKERY=ifelse(SITE.TYPE %in% c('R','Y/R'),1,0)) %>% 
  ungroup()
```

View.
```{r}
bc_sf <- bc_long %>% st_as_sf(coords=c('LONGITUDE','LATITUDE'), crs=4326)
bc_bbox <- bc_sf %>% st_bbox()

bc_sf %>% filter(STAGE=='COUNT.NON.PUP') %>%
  ggplot()+
  geom_sf(data=coast_sf)+
  geom_sf(aes(color=COUNTS, shape = factor(ROOKERY)), size=2)+
  scale_color_viridis()+
  coord_sf(xlim=c(bc_bbox$xmin,bc_bbox$xmax), ylim=c(bc_bbox$ymin,bc_bbox$ymax))+
  theme_minimal()+
  facet_wrap(~SURVEY.YEAR)+
  labs(title='Steller sea lion haulouts and rookeries in British Columbia')
```

We need to use data from the same period, although there are fewer sampling years in the BC data from the 1990's (1992, 1994, 1998). Take averages. Work only with non-pups.
```{r}
nonpup_avg_bc <- bc_sf %>% filter(STAGE=='COUNT.NON.PUP' & SURVEY.YEAR %in% c(1992,1994,1998)) %>%
  group_by(REGION,SITE,ROOKERY) %>% 
  summarise(COUNTS=mean(COUNTS,na.rm=TRUE)) %>%
  ungroup()

# NaN where all counts in the 1990's were NA's. Drop those altogether
nonpup_avg_bc <- nonpup_avg_bc %>% filter(!is.nan(COUNTS))

nonpup_avg_bc %>% ggplot()+
  geom_sf(data=coast_sf)+
  geom_sf(aes(color=COUNTS, shape = factor(ROOKERY)), size=3)+
  scale_color_viridis()+
  coord_sf(xlim=c(bc_bbox$xmin,bc_bbox$xmax), ylim=c(bc_bbox$ymin,bc_bbox$ymax))+
  theme_minimal()+
  labs(title='Steller sea lion haulouts and rookeries in British Columbia')
```

## Stitch AK and BC data

Rearrange the BC data so that it can be stitched to the AK data, then bind the two data frames. Note that here we are not considering potential bias in the methods between AK and BC, and also there are different sampling years between the two.
```{r}
nonpup_avg_bc <- nonpup_avg_bc %>% 
  select(SITE,REGION,ROOKERY,COUNTS) %>%
  mutate(REGION='BC')

# bind
nonpup_avg <- rbind(nonpup_avg_ak,nonpup_avg_bc)

# view
p <- nonpup_avg %>% st_transform(crs=atlantis_crs) %>% 
  ggplot()+
  geom_sf(data=coast_sf)+
  geom_sf(aes(color=log1p(COUNTS),shape=factor(ROOKERY)), size=2)+
  scale_color_viridis()+
  coord_sf(xlim=c(atlantis_bbox$xmin, atlantis_bbox$xmax),ylim=c(atlantis_bbox$ymin, atlantis_bbox$ymax+50000))+
  theme_minimal()+
  labs(title='Steller sea lions haulouts and rookeries in the GOA',color='Log-counts')

p

# ggsave('colonies.png',p,width=10,height=5,unit='in')
```

# Summer distributions

Incorporate the different dispersal from rookery vs haulout here. We use values of foraging trip distance from haulout for summer and winter adult females here as a first crude approximation of movements from rookeries (where the pups are) and haulouts. This is more of a placeholder for now, and we will need to account for sex ratio (assume males can move farther than pupping females), proportion of breeders (not all females will be pupping), age structure (pups, juveniles and adults have different dispersal), and season (they travel farther in winter) at the colony. Even that will be an approximation, for example (some?) males in the summer haul out and fast. For now the below is to say that SSL do not move far from rookeries because the pups are there, but move far from haulouts because they are non-reproductive sites. 

These will be for S2 and S3.
```{r}
dist_rookery <- 17*1000 #m # average summer female trip distance from Merrick and Loughlin (1997) 
dist_haulout <- 133*1000 #m average winter female trip distance from Merrick and Loughlin (1997)

ssl_colonies <- nonpup_avg %>% 
  st_transform(crs=atlantis_crs) %>% 
  rowwise() %>% 
  mutate(foraging_distance=ifelse(ROOKERY==1,dist_rookery,dist_haulout)) 

ssl_colonies <-ssl_colonies %>% 
  st_buffer(dist=ssl_colonies$foraging_distance) %>% 
  ungroup()

coast_sf <- coast_sf %>% st_transform(crs=atlantis_crs)

# intersect each colony with the coast data

colony_at_sea <- ssl_colonies %>% st_difference(coast_sf) # this takes time

p1 <- colony_at_sea %>% ggplot()+
  geom_sf(aes(fill=log1p(COUNTS)),alpha=0.5)+
  scale_fill_viridis()+
  geom_sf(data=coast_sf)+
  coord_sf(xlim=c(atlantis_bbox$xmin, atlantis_bbox$xmax),ylim=c(atlantis_bbox$ymin, atlantis_bbox$ymax+50000))+
  theme_minimal()+
  labs(title='Steller sea lions based on summer and winter dispersal',fill='Log-counts')

p1

# ggsave('ranges_from_colonies.png',p1,width=10,height=5,unit='in')
```

Now compute the area for each of those buffers.
```{r}
colony_at_sea <- colony_at_sea %>% mutate(colony_area_at_sea=st_area(colony_at_sea))
```

Write a function that takes each individual colony geometry and does st_intersect() with each Atlantis box. Bound to take a very long time.
```{r, warning=FALSE}
# shed some variables
box_thin <- atlantis_box %>% select(.bx0,botz,boundary)

# calculate the area of the intersection with each atlantis box in the model, and scale the n of ind for that colony by the area of the intersection. Do not consider island boxes, because those count as land, but do consider boundary boxes.
box_colony_overlap <- function(this_colony,colony_data,box_data){
  
  box_data <- box_data %>% filter(botz<0)
  
  colony_data <- colony_data %>% filter(SITE==this_colony)
  
  this_intersection <- box_data %>% st_intersection(colony_data) # intersection between the box and the colony
  this_intersection <- this_intersection %>% 
    mutate(colony_box_area = st_area(this_intersection), # area of the intersection
           proportion_of_colony_area = as.numeric(colony_box_area/colony_area_at_sea), # proportion of intersection to tot colony area
           abundance_this_box = proportion_of_colony_area*COUNTS) %>% # attribute to this box the animals from this colony based on the calc'ed proportion
    st_set_geometry(NULL) 
    
  return(this_intersection)
}

all_IDs <- unique(colony_at_sea$SITE)

atlantis_abundances <- rbindlist(purrr::map(all_IDs,box_colony_overlap,colony_data=colony_at_sea,box_data=box_thin))
```

Do a quick check that the abundances adds up (i.e. no cases where the disaggregated abundance by box is higher than the original abundance of the colony.)
```{r}
# check <- atlantis_abundances %>% 
#   group_by(SITE,COUNTS) %>% 
#   summarise(test = sum(abundance_this_box)) %>% 
#   ungroup() %>% 
#   mutate(diff=COUNTS-test)
```
Seems to be in order - only cases where the biomass exceeds the box biomass because the radius of the colony spans outside the model domain.

Add up abundances by box.
```{r}
atlantis_abundances$abundance_this_box[is.nan(atlantis_abundances$abundance_this_box)] <- NA

abundance_by_box <- atlantis_abundances %>% group_by(.bx0) %>% summarise(abundance = sum(abundance_this_box,na.rm=TRUE)) %>% ungroup()
```

Join with box set again for the geometry and map.
```{r}
atlantis_ssl <- atlantis_box %>% select(.bx0,botz,area,boundary) %>% left_join(abundance_by_box, by = '.bx0') %>%
  mutate(log_abundance = log1p(abundance),
         density = abundance/area*1000000, # back to km2
         logdensity = log1p(density)) 

p2 <- atlantis_ssl %>% 
  rowwise() %>%
  mutate(abundance = ifelse(isTRUE(boundary),NA,abundance)) %>%
  ungroup() %>%
  ggplot()+
  geom_sf(aes(fill=logdensity))+ # back to km2
  scale_fill_viridis()+
  geom_sf(data=coast_sf, fill = 'grey')+
  coord_sf(xlim = c(atlantis_bbox$xmin, atlantis_bbox$xmax), ylim = c(atlantis_bbox$ymin, atlantis_bbox$ymax))+
  theme_bw()+
  labs(title='Steller sea lions in Atlantis GOA', fill = expression(paste('Logdensity \n (ind ',km^-2, ')')))
p2

# ggsave('ssl_box.png',p2,width=10,height=5,unit='in')
```

Results depend on the foraging range. 

# Winter distributions

Assume that all animals (the same amount) move with their winter range for S1 and S4.
```{r}
dist_colony <- 133*1000 #m average winter female trip distance from Merrick and Loughlin (1997)

ssl_colonies_winter <- nonpup_avg %>% 
  st_transform(crs=atlantis_crs) %>% 
  rowwise() %>% 
  mutate(foraging_distance=dist_colony) 

ssl_colonies_winter <-ssl_colonies_winter %>% 
  st_buffer(dist=ssl_colonies_winter$foraging_distance) %>% 
  ungroup()

# intersect each colony with the coast data

colony_at_sea_winter <- ssl_colonies_winter %>% st_difference(coast_sf) # this takes time

p2 <- colony_at_sea_winter %>% ggplot()+
  geom_sf(aes(fill=log1p(COUNTS)),alpha=0.5)+
  scale_fill_viridis()+
  geom_sf(data=coast_sf)+
  coord_sf(xlim=c(atlantis_bbox$xmin, atlantis_bbox$xmax),ylim=c(atlantis_bbox$ymin, atlantis_bbox$ymax+50000))+
  theme_minimal()+
  labs(title='Steller sea lions based on winter dispersal',fill='Log-counts')

p2

# ggsave('ranges_from_colonies.png',p1,width=10,height=5,unit='in')
```

Now compute the area for each of those buffers.
```{r}
colony_at_sea_winter <- colony_at_sea_winter %>% mutate(colony_area_at_sea=st_area(colony_at_sea_winter))
```

Calculate overlap based on function above.
```{r, warning=FALSE}
atlantis_abundances_winter <- rbindlist(purrr::map(all_IDs,box_colony_overlap,colony_data=colony_at_sea_winter,box_data=box_thin))
```

Add up abundances by box.
```{r}
atlantis_abundances_winter$abundance_this_box[is.nan(atlantis_abundances_winter$abundance_this_box)] <- NA

abundance_by_box_winter <- atlantis_abundances_winter %>% group_by(.bx0) %>% summarise(abundance = sum(abundance_this_box,na.rm=TRUE)) %>% ungroup()
```

Join with box set again for the geometry and map.
```{r}
atlantis_ssl_winter <- atlantis_box %>% select(.bx0,botz,area,boundary) %>% left_join(abundance_by_box_winter, by = '.bx0') %>%
  mutate(log_abundance = log1p(abundance),
         density = abundance/area*1000000, # back to km2
         logdensity = log1p(density)) 

p3 <- atlantis_ssl_winter %>% 
  rowwise() %>%
  mutate(abundance = ifelse(isTRUE(boundary),NA,abundance)) %>%
  ungroup() %>%
  ggplot()+
  geom_sf(aes(fill=logdensity))+ # back to km2
  scale_fill_viridis()+
  geom_sf(data=coast_sf, fill = 'grey')+
  coord_sf(xlim = c(atlantis_bbox$xmin, atlantis_bbox$xmax), ylim = c(atlantis_bbox$ymin, atlantis_bbox$ymax))+
  theme_bw()+
  labs(title='Steller sea lions in Atlantis GOA', fill = expression(paste('Logdensity \n (ind ',km^-2, ')')))
p3

# ggsave('ssl_box.png',p2,width=10,height=5,unit='in')
```

Write out summer and winter distributions. Zero out the abundances in boundary boxes and island boxes.
```{r}
s2_s3 <- atlantis_ssl %>% 
  select(.bx0,botz,boundary,abundance) %>% 
  st_set_geometry(NULL) %>% 
  rowwise() %>%
  mutate(abundance = ifelse(isTRUE(boundary) | botz==0,0,abundance)) %>%
  ungroup() %>%
  mutate(prop=abundance/sum(abundance,na.rm=T)) %>% 
  select(-botz,-boundary,-abundance)

s1_s4 <- atlantis_ssl_winter %>% 
  select(.bx0,botz,boundary,abundance) %>% 
  st_set_geometry(NULL) %>% 
  rowwise() %>%
  mutate(abundance = ifelse(isTRUE(boundary) | botz==0,0,abundance)) %>%
  ungroup() %>%
  mutate(prop=abundance/sum(abundance,na.rm=T)) %>% 
  select(-botz,-boundary,-abundance)

# turn NAs to 0 for now
s2_s3[is.na(s2_s3)] <- 0
s1_s4[is.na(s1_s4)] <- 0

# write out
write.csv(s2_s3, '../output/ssl_s2_s3.csv', row.names = F)
write.csv(s1_s4, '../output/ssl_s1_s4.csv', row.names = F)
```

At the moment we are assuming that juveniles and adults have the same spatial distributions.